Course Project
==============
This is how I complete this project.

1. Loading and preprocessing the data
```{r}
activity<-read.csv("C:/Users/AAA/Documents/R/activity.csv",colClasses = c("numeric","Date","numeric"))
```

2. The mean total number of steps taken per day.

(1). Calculate the total number of steps taken per day
```{r}
library(dplyr)
total_steps<-group_by(activity,date)
total_steps<-summarise(total_steps,sum=sum(steps))
total_steps<-subset(total_steps,!is.na(sum))
head(total_steps)
```

(2). The histogram of the total number of steps taken each day
```{r}
hist(total_steps$sum,main="Total Steps",xlab="Steps")
```

(3). The mean and median of the total number of steps taken per day
```{r results='hide'}
mean<-mean(total_steps$sum)
median<-median(total_steps$sum)
```

The mean is `r mean`. The median is `r median`.

3. The average daily activity pattern

(1). Time series plot 
```{r}
five_minute<-group_by(activity,interval)
five_minute<-summarise(five_minute,ave=sum(steps,na.rm = T)/length(unique(activity$date)))
plot(five_minute,type="l",main="Time series plot")
```

(2). The maximum number of steps in 5-minute interval
```{r,results='hide'}
max<-as.numeric(five_minute[with(five_minute,which.max(ave)),1])
```

 The maximum number of steps is in `r max`.
 
 4. Imputing missing values
 (1). The total number of missing values in the dataset 
 ```{r,results='hide'}
 missing<-sum(is.na(activity$steps))
 ```
 The total number of missing values in the dataset is `r missing`.
 
 (2). Filling in all of the missing values in the dataset
```{r}
nas<-which(is.na(activity$steps))
na_replaced<-activity
for (i in nas){
        num<-which(five_minute$interval==na_replaced$interval[i])
        na_replaced$steps[i]<-five_minute$ave[num]
}
```

(3). The new dataset
```{r}
head(na_replaced)
```

(4). Histogram, mean, and median
```{r}
total_steps_new<-group_by(na_replaced,date)
total_steps_new<-summarise(total_steps_new,sum=sum(steps))
hist(total_steps_new$sum,main="Total Steps",xlab="Steps")
```
```{r,results='hide'}
mn<-mean(total_steps_new$sum)
md<-median(total_steps_new$sum)
```
The mean is `r mean`. The median is `r median`.

5. Activity patterns between weekdays and weekends

(1). Create a new factor variable in the dataset indicating whether a given date is a weekday or weekend day
```{r}
Sys.setlocale(category = "LC_ALL", locale = "english")
weekdata<-mutate(na_replaced,week=weekdays(na_replaced$date))
for (i in 1:nrow(weekdata)){
        if (weekdata$week[i]=="Saturday"|weekdata$week[i]=="Sunday"){
                weekdata$week[i]<-"weekend"
        }
        else weekdata$week[i]<-"weekday"
}
weekdata$week<-as.factor(weekdata$week)
```

(2). Panel plot
```{r}
week<-group_by(weekdata,interval,week)
total_week<-summarise(week,sum=mean(steps))
library(ggplot2)
g<-ggplot(total_week,aes(interval,sum))
g+geom_line()+facet_grid(week~.)
```